MLH1 data report 

### 2017-11-02 rmd_report.rmd
cleaning up rmd report file

latice plot of scatter plots for jitter plots of cell oberservations by quality. The category mean is in black and the mouse specific mean is in red.
```{r, echo=FALSE, include=FALSE, message=FALSE, warning=FALSE}
#TODO, add a line for mouse and strain

#this creates a slot for CAST female, but no data
#each of the indiviual dataframes can be acessed with df_list$ ---- category
# for each sub-data frame, make mouse specific table,
#
#add mouse mean to the df
df_list <- split(MLH1_data, as.factor(MLH1_data$category))

o=0
i=0

@@

```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE }
#geom_hline(aes(yintercept = med, group = gr), colour = 'red')
#for (gg in 1:length(plot_list) ){
#  show(plot_list[gg])
  #invisible(lapply(obj,function(x) plot(x,main="some plot")))
#}
```

>>>>

latice plot of scatter plots for jitter plots of cell oberservations by quality. The category mean is in black and the mouse specific mean is in red.
```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE}
#what is the purpose of this block

df_list <- split(MLH1_data, (MLH1_data$category))

#remove sections which are in category but have no data
df_list <- df_list[ -c(7, 12, 14,16, 18) ]
#7, PERC. 12 CASTF, 14 HMI f , 16 SPRET f. 18 other

df_list 
o=0
i=0

@@

```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE }
geom_hline(aes(yintercept = med, group = gr), colour = 'red')
for (gg in 1:length(plot_list) ){
  show(plot_list[gg])
  #invisible(lapply(obj, function(x) plot(x,main="some plot")))
}
```
